Using Genetic Algorithms to Find Approximations for the Minimum Vertex Cover Problem

### 2018-02-28 paper.tex
fixed upper/lower cases typos

The outline of this paper is as follows: Firstly, Section~\ref{sec:ga} gives a
short introduction to genetic algorithms, and explains briefly how they work.
Section~\ref{sec:mvcp} introduces the mvcp with two of its main heuristics,
and explains its representation for an application of the genetic algorithm.
Lastly, Section~\ref{sec:exper} presents our experimental results and
points out the notable observations that can be drawn from these results.

@@

\caption[average fitness value plotted against edge density]
{%
average fitness value found by GA and vercov heuristic plotted
against the edge density for each random graph in test set~1 (the left figure) or~2
(the right figure).%
}
\label{fig:av}
\end{figure}

>>>>

The outline of this paper is as follows: Firstly, section~\ref{sec:ga} gives a
short introduction to genetic algorithms, and explains briefly how they work.
Section~\ref{sec:mvcp} introduces the mvcp with two of its main heuristics,
and explains its representation for an application of the genetic algorithm.
Lastly, section~\ref{sec:exper} presents our experimental results and
points out the notable observations that can be drawn from these results.

@@

\caption[Average fitness value plotted against edge density]
{%
Average fitness value found by GA and vercov heuristic plotted
against the edge density
for each random graph in test set~1 (the left figure) and
for each random graph in test set~2 (the right figure).%
}
\label{fig:av}
\end{figure}
